First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-01-19 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
updating the experimental setup and some of the figures

%introduction
The GPDs are defined for each quark flavor and gluon as matrix
elements of the light cone operators \cite{Belitsky}, describing the transition 
between the initial and final states of a hadron. The GPDs depend on two 
longitudinal momentum fraction variables ($x$, $\xi$) and on the momentum 
transfer $t$ to the target. $x$ is the average longitudinal momentum fraction 
of the parton involved in the process and $\xi$ is the longitudinal fraction of 
the momentum transfer $t$, which is related to the Bjorken variable $x_{B}$: 
$\xi\approx {{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$ with
the proton mass $M$ and $\nu=E_e-E_{e^\prime}$. The GPDs $x$ variable cannot be 
measured experimentally in a DVCS reaction. Hence, we measure the GPDs 
convolutions on $x$, the so-called Compton Form Factors (CFF) 
\cite{Guidal:2013rya}.  In a DVCS process, the number of GPDs needed to 
parametrize the partonic structure of a hadron depends on the different 
configurations between the spin of the hadron and the helicity direction of the 
struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
chose the $^4$He nucleus as our target of interest because of it's spinless 
nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
high density and it is a well-known few-body system.

The study of nuclear DVCS is still in its infancy due to the challenging 
detection of the low-energy recoil nuclei in fixed target experiments. Until 
very recently, the HERMES experiment \cite{Ellinghaus:2002zw} was the only one 
to measure DVCS off heavier nuclei such as $^4$He, N, Ne, Kr and Xe, where only 
the scattered electron and the real photon are detected. In this paper, we 
report the first exclusive measurements of coherent DVCS channel off $^4$He 
where all products of the reaction are detected including the recoiling $^4$He 
nucleus. The incoherent DVCS channel measurement from the same data set in in 
preparation and will reported in another publication.

@@

@@

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/updated_CFFs.pdf}
\vspace{-0.9cm}
\caption{The model-independent extraction of the imaginary (blue points) and
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
\label{fig:CFF_HA}
\end{figure}

>>>>

%introduction
The GPDs are defined for each quark flavor and gluon as matrix
elements of the light cone operators \cite{Belitsky}, describing the transition 
between the initial and final states of a hadron. The GPDs depend on two 
longitudinal momentum fraction variables ($x$, $\xi$) and on the momentum 
transfer $t$ to the target. $x$ is the average longitudinal momentum fraction 
of the parton involved in the process and $\xi$ is the longitudinal fraction of 
the momentum transfer $t$, which is related to the Bjorken variable $x_{B}$: 
$\xi\approx {{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$ with
the proton mass $M$ and $\nu=E_e-E_{e^\prime}$. The GPDs $x$ variable cannot be 
measured experimentally in a DVCS reaction. Hence, we measure the their 
convolutions on $x$, the so-called Compton Form Factors (CFF) 
\cite{Guidal:2013rya}.  In a DVCS process, the number of GPDs needed to 
parametrize the partonic structure of a hadron depends on the different 
configurations between the spin of the hadron and the helicity direction of the 
struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
chose the $^4$He nucleus as our target of interest because of it's spinless 
nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
high density and it is a well-known few-body system.

The study of nuclear DVCS is still in its infancy due to the challenging 
detection of the low-energy recoil nuclei in fixed target experiments. Until 
very recently, the HERMES experiment \cite{Ellinghaus:2002zw} was the only one 
to measure DVCS off heavier nuclei such as $^4$He, N, Ne, Kr and Xe, where only 
the scattered electron and the real photon are detected. In this paper, we 
report the first exclusive measurements of the coherent DVCS channel off $^4$He 
where all products of the reaction are detected including the recoiling $^4$He 
nucleus. Following this exclusive measurement, the $^4$He CFF 
($\mathcal{H}_{A}$) will be extracted experimentally in a fully model 
independent way for the first time ever. The incoherent DVCS channel 
measurement from the same data set in in preparation and will reported in 
another publication.

@@

The experiment, CLAS-EG6, took place the experimental Hall-B of Jefferson 
labortory (JLab) in 2009.  JLab delivers a nearly 100\% duty factor, 6~GeV 
linearly polarized electrons into three experimental halls. The data were 
collected over three months via projecting a 6.064 GeV longitudinally ploarized 
beam, (83$\%$ polarization), on a 6 atm gasous $^4$He target, 20 cm long. The 
CEBAF Large Acceptance Spectrometer (CLAS) was upgraded during the CLAS-EG6 
running. This detector is large acceptance covering nearly 2$\pi$ and is 
composed of drift chambers, Cherenkov counters, scintillator counters and an 
electro-magnetic calorimeter. It allows to detect accurately electrons which 
provide the trigger for the experiment. It is complemented for DVCS experiments 
with an inner electro-magnetic calorimeter made of PbWO crystals to detect the 
photons emitted at low angle and with a solenoid to keep the Moller electrons 
produced along the beam line to get into our detectors.

In order to ensure the coherence of the process, we also detect the recoiling 
helium-4 nuclei. We built a small and light radial time projection chamber 
(RTPC) to detect recoiling helium nuclei down to energies of few MeVs. The 
chamber, shown in figure~\ref{fig:rtpc}, is surrounding the gaseous target 
filled with 6~atm helium-4 and is 20 cm long with a 3 cm radial drift 
length. The detector was specifically calibrated for helium-4 nuclei using 
elastic scattering produced with a 1.2~GeV electron beam.
To ensure that the process is exclusive, we apply cuts on 
several kinematic variables (figure~\ref{fig:exclu}) such as missing energy,
mass and momentum. The cuts are chosen to represent consistently 3 half width 
at half maximum in order to avoid any bias in the selection.

@@

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/Coherent_CFF.pdf}
\vspace{-0.9cm}
\caption{The model-independent extraction of the imaginary (blue points) and
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
\label{fig:CFF_HA}
\end{figure}
